Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-08-20 documentation/paper.tex
Lots of fairly minor edits

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}

@@

\begin{abstract}
    Background radiation is a major hurdle to overcome for bubble chamber dark matter experiments such as PICO-60. The current practice of manually developing a discriminator function to eliminate background data is difficult when calibration data is frequently impure and present only in small quantities. In this study, several different input formats and neural network architectures are applied to the task. First, they are optimized in a supervised learning context. Next, novel semi-supervised learning algorithms are trained, and found to replicate the Acoustic Parameter discriminator previously used in PICO-60 with up to 100\% accuracy.
\end{abstract}

@@

In the PICO-60 experiment, and in most other experiments for dark matter detection, one of the most important and challenging hurdles to overcome is that of background radiation. Unwanted particles from a variety of sources can produce event signatures that appear very similar to those of dark matter candidates.

To resolve this, physicists must determine a discriminator function that can, based on some sensory data, separate dark matter candidates from background radiation. Two general problems stand in the way:

\begin{enumerate}
    \item A detailed model of the physical environment is often used to produce an accurate discriminator. This takes a long time even for a team of experienced physicists, and will have to be updated whenever the physical variables of the experimental apparatus change.

    \item The primary intention of many dark matter experiments, which is to reduce background radiation to the lowest level possible, means that there will be a very small number of background events detected. This places a severe limit on the amount of data that is available to optimize such a discriminator.

@@

The benefit to experimental science would be to potentially allow the creation of a discriminator in cases where it would be difficult to construct one by conventional means. There may be various reasons for this:

@@

The PICO-60 bubble chamber experiment for detection of weakly interacting massive particles (WIMPs) \cite{pico} was completed in 2017. It provides an excellent basis on which to develop and test the efficacy of such techniques as a potential tool for event discrimination, relative to the conventional techniques used during initial analysis of the experiment.

WIMP candidates in the cross section and mass ranges that the PICO-60 detector is sensitive to are predicted to produce nuclear recoils with the same properties as those created by neutrons. The key difference is that neutrons frequently (but not always) scatter and produce multiple bubbles, where the extremely small predicted cross sections of WIMP candidates mean that they should almost invariably create just one bubble. This means single-bubble neutron events can be used to optimize a discriminator to detect WIMP events.

@@

Acoustic Parameter is the technique that was used for event discrimination in the original PICO-60 analysis. It is a function that discriminates between alpha particles and nuclear recoils based on audio data. It was derived based on a physical model of the bubble chamber, and was tuned using calibration runs using neutron sources to produce events in the PICO-60 apparatus.

Before Acoustic Parameter can be calculated, the audio data must first be converted into the frequency domain (specifically, with the banded Fourier transform $\beta_{8}$). It must also be preprocessed with the position correction function $PosCor(\beta_{8}, \chi)$, which adjusts the overall volume of an audio recording according to its position in the vessel. This is done because the resonance characteristics differ significantly depending on the position of an event.

@@

The lowest-level data derived from the piezos is the raw waveform $\omega$. This consists of a series of samples collected every 400,000\textsuperscript{th} of a second. They are each represented as a 16-bit integer. Only the section of the audio between sample 90,000 (inclusive) and sample 190,000 (exclusive) was used during most experiments, because before this there is background noise, and afterwards there is a clipped signal produced by hydraulics repressurizing the vessel. (These sections contain no information and can be undesirably fit on by neural networks.)

@@

The raw waveform $\omega$ was converted into the frequency domain by means of a one-dimensional Discrete Fourier Transform for real input. Since DFTs produce sequences of complex numbers, the magnitude of each element was computed. The full-resolution Fourier transform $\beta _{50,001}$ consists of a sequence of complex numbers, half the length of the raw waveform $\omega$.

Beyond this, the banded Fourier transform $\beta_{8}$ (which is the input to Acoustic Parameter and the original neural analysis) was computed by integrating the resonant energy over all frequencies within each of a set of bands. This can be thought of as a method of signal downscaling, compressing the signal into a smaller number of data points.

@@

For each event that is captured, the four cameras within the PICO-60 apparatus each capture a sequence of 71 images before and after formation of a bubble is detected. These raw images contain a large amount of extraneous information; they encompass the entire vessel. To reduce the input information, the image window sequence $\iota$ includes 50\texttimes50 cropped windows around the position of the bubble. The 71 frames, many of which contain either no bubble or a bubble in later stages of formation, are reduced to 10 immediately around the formation of the bubble. $\iota$ includes five frames from before the recording trigger, because the bubble does not cause a trigger until it is already at a significant size.

@@

\begin{itemize}
    \item The run was not collected during engineering or testing ($\texttt{run\_type}\neq99$)
    \item Recording was triggered by the camera ($\texttt{trigger\_main}=0$)
    \item Acoustic Parameter is not erroneously large and negative ($log_{10}(\texttt{acoustic\_bubnum})>-100$)
    \item Recorded more than 25 seconds after reaching target pressure ($\texttt{te}>25$)
    \item The bubble position $\chi$ was successfully calculated ($[\chi_{X}, \chi_{Y}, \chi_{Z}]\neq[-100, -100, -100]$)
\end{itemize}

@@

\begin{itemize}
    \item Either 0 or 1 bubbles are detected based on images from the camera ($\texttt{nbub}<2$)
    \item The number of bubbles approximated using the pressure transducer is close to 1 ($0.7<\texttt{dytranCZ}<1.3$)
\end{itemize}

@@

\begin{itemize}
    \item The fiducial cut $FidWallCut(D)$ defines a spatial area along the walls of the vessel within which no events are accepted. It determines whether events fall within this area based on the visually calculated position $\chi$.
    \item The pressure cut $PresWallCut(D)$ restricts the pressure detected by the pressure transducer, without any position corrections, to be close to 1 ($0.7<\texttt{dytranC}<1.3$).
    \item The acoustic cut $AcWallCut(D)$ is defined using the banded Fourier transform $\beta_{8}$, and takes advantage of differences in the frequency distribution (specifically the first and second frequency bands of the first and third piezos) of wall events and non-wall events.
\end{itemize}

@@

\begin{itemize}
    \item Supervised learning, in which a system is trained on a set of fully-labeled data to classify unseen examples according to the patterns it observes in the training set.
    \item Unsupervised learning, in which a system finds patterns or clusters in a set of unlabeled data. This can find order in almost any training set, but it is unpredictable and may not find the particular patterns desired.
\end{itemize}

A significant challenge in this application is that neither supervised nor unsupervised learning is ideal. The calibration sets available for training are not pure, so supervised learning is likely to overfit on biases and produce undesirable results. Conversely, unsupervised learning may be able to find clusters in the data, but it is impossible to guarantee it will distinguish between nuclear recoils and alpha particles as opposed to some other binary separation.

@@

Each of the learning algorithms used in this study applies a neural network. For each of the general configurations (multi-layer perceptron, one-dimensional convolutional neural network, et cetera) there are many possible specific architectures with different hyperparameters, which have to be optimized to improve performance. Some examples of hyperparameters are:

\begin{itemize}
    \item Number of layers of each type (dense, convolutional)
    \item Number of neurons in dense layers
    \item Number of filters, kernel size, and stride in convolutional layers
    \item Types and amounts of regularization to apply (L2, dropout \cite{dropout})
\end{itemize}

@@

Except where specifically mentioned, $WallCut(D)$ was not applied. This was done for 2 reasons:

@@

All supervised learning configurations were trained and evaluated based on their ability to discriminate calibration runs (predominantly neutrons) from background runs (predominantly alpha particles). This was used instead of Acoustic Parameter for two reasons:

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{waveform_hist}
    \caption{\label{waveform_hist} Prediction distribution of the best $DeepConvWithPos(\omega, \chi)$ discriminator without $WallCut(D)$.}
\end{figure}

@@

With $WallCut(D)$:

\begin{tabular}{|l|l|l|l|l|l|l|}
    \hline
    L2 $\lambda$ & Dropout & Filters & Kernel Size & \# Layers Multiplier & Max Accuracy & Class-Wise Std Dev \\
    \hline
    0.003 & 0 & 24 & 3 & 3 & 95\% & 0.44 \\
    \hline
    0.003 & 0 & 48 & 5 & 3 & 96\% & 0.41 \\
    \hline
    0.003 & 0.5 & 24 & 5 & 3 & 93\% & 0.50 \\
    \hline
    0.001 & 0 & 48 & 5 & 3 & 95\% & 0.48 \\
    \hline
    0.001 & 0.25 & 48 & 3 & 6 & 93\% & 0.62 \\
    \hline
    0.0003 & 0.5 & 24 & 5 & 6 & 95\% & 0.49 \\
    \hline
\end{tabular}

Without $WallCut(D)$:

\begin{tabular}{|l|l|l|l|l|l|l|}
    \hline
    L2 $\lambda$ & Dropout & Filters & Kernel Size & \# Layers Multiplier & Max Accuracy & Class-Wise Std Dev \\
    \hline
    0.003 & 0 & 24 & 3 & 3 & 91\% & 0.61 \\
    \hline
    0.003 & 0.5 & 24 & 5 & 3 & 91\% & 0.65 \\
    \hline
    0.001 & 0.25 & 24 & 3 & 3 & 91\% & 0.66 \\
    \hline
    0.001 & 0.5 & 48 & 5 & 3 & 88\% & 0.73 \\
    \hline
    0.0003 & 0 & 48 & 5 & 6 & 78\% & 0.95 \\
    \hline
    0.0003 & 0.5 & 48 & 5 & 6 & 74\% & 0.92 \\
    \hline
\end{tabular}

@@

In addition to the Fourier transform used in the original PICO-60 analysis, higher resolutions were computed by similar means. These included $\beta _{5}$, $\beta _{10}$, $\beta _{20}$, and $\beta _{40}$. Also, the full-resolution $\beta _{50,001}$ was input into a neural network directly, without any downscaling.

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{banded_no_pos_input_hist}
    \caption{\label{banded_no_pos_input_hist} Prediction distribution of the best $FourierMLP(\beta_{8})$ discriminator, with $WallCut(D)$.}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{high_freq_no_wall_hist}
    \caption{\label{high_freq_no_wall_hist} Prediction distribution of the best $FourierMLPWithPos(\beta_{50,001}, \chi)$ discriminator, without $WallCut(D)$.}
\end{figure}

@@

With $WallCut(D)$:

\begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Configuration & L2 $\lambda$ & Dropout & Layers & Max Accuracy & Class-Wise Std Dev \\
    \hline
    $FourierMLP(PosCor(\beta_{8}))$ & 0 & 0.5 & 2 & 95\% & 0.56 \\
    \hline
    $FourierMLP(\beta_{8})$ & 0 & 0.5 & 2 & 98\% & 0.29 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.5 & 3 & 95\% & 0.44 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.25 & 3 & 97\% & 0.43 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 0.003 & 0.25 & 3 & 93\% & 0.54 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 94\% & 0.52 \\
    \hline
    $FourierMLPWithPos(\beta_{40}, \chi)$ & 0 & 0 & 3 & 91\% & 0.57 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.0003 & 0 & 4 & 91\% & 0.53 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.25 & 4 & 91\% & 0.56 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.5 & 3 & 89\% & 0.64 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 4 & 89\% & 0.65 \\
    \hline
\end{tabular}

It is very clear here that higher resolutions do not improve accuracy. Regularization, both dropout and L2, appears to have relatively little effect.

Without $WallCut(D)$:

\begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Configuration & L2 $\lambda$ & Dropout & Layers & Max Accuracy & Class-Wise Std Dev \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 92\% & 0.63 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0 & 0 & 3 & 95\% & 0.49 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0 & 2 & 96\% & 0.47 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0 & 2 & 97\% & 0.47 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.25 & 2 & 95\% & 0.54 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 2 & 94\% & 0.53 \\
    \hline
\end{tabular}

@@

The following table shows performance of various configurations of $ImageConv(\iota)$:

\begin{tabular}{|l|l|l|l|l|l|}
    \hline
    L2 $\lambda$ & Dropout & Convolutional Layers & Dense Layers & Max Accuracy & Class-Wise Std Dev \\
    \hline
    0 & 0.5 & 4 & 3 & 77\% & 1.01 \\
    \hline
    0 & 0.25 & 4 & 3 & 85\% & 0.95 \\
    \hline
    0.01 & 0.25 & 4 & 3 & 66\% & 0.97 \\
    \hline
    0.003 & 0.25 & 4 & 3 & 69\% & 0.97 \\
    \hline
    0.01 & 0.25 & 12 & 3 & 66\% & 0.98 \\
    \hline
    0.01 & 0.5 & 12 & 3 & 68\% & 0.99 \\
    \hline
\end{tabular}

@@

With $WallCut(D)$:

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $FourierMLP(PosCor(\beta_{8}), \chi)$ & 97\% & 0.42 \\
    \hline
    $FourierMLP(\beta_{8})$ & 98\% & 0.29 \\
    \hline
    $FourierMLPWithPos(\beta_{8}, \chi)$ & 95\% & 0.44 \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 94\% & 0.52 \\
    \hline
    $FourierMLPWithPos(\beta_{40}, \chi)$ & 91\% & 0.54 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 91\% & 0.53 \\
    \hline
    Original PICO-60 Neural Network & 94\% & 0.99 \\
    \hline
\end{tabular}

Without $WallCut(D)$:

\begin{tabular}{|l|l|l|}
    \hline
    Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
    \hline
    $FourierMLPWithPos(\beta_{20}, \chi)$ & 92\% & 0.63 \\
    \hline
    $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 97\% & 0.47 \\
    \hline
    $DeepConv(\omega)$ & 77\% & 0.86 \\
    \hline
    $DeepConvWithPos(\omega, \chi)$ & 91\% & 0.61 \\
    \hline
    $ImageConv(\iota)$ & 85\% & 0.95 \\
    \hline
\end{tabular}

>>>>

\usepackage[margin=1in]{geometry}
\usepackage{textcomp}
\usepackage{parskip}
\usepackage{amsmath}
\usepackage[backend=biber, style=alphabetic, sorting=ynt]{biblatex}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{caption}

@@

\begin{abstract}
    The identification of non-signal events is a major hurdle to overcome for bubble chamber dark matter experiments such as PICO-60. The current practice of manually developing a discriminator function to eliminate background events is difficult when calibration data is frequently impure and present only in small quantities. In this study, several different input formats and neural network architectures are applied to the task. First, they are optimized in a supervised learning context. Next, novel semi-supervised learning algorithms are trained, and found to replicate the Acoustic Parameter discriminator previously used in PICO-60 with up to 100\% accuracy.
\end{abstract}

@@

In the PICO-60 experiment, and in most other experiments striving to directly detect dark matter, one of the most important and challenging hurdles to overcome is that of background events. Unwanted particles from a variety of sources can produce event signatures that appear very similar to those which are expected to be created by dark matter candidates.

To resolve this, physicists must determine a discriminator function that can, based on experimental data, separate events generated by possible dark matter candidates from those due to background radiation. Two general problems stand in the way:

\begin{enumerate}
    \item A detailed model of the physical environment is often used to produce an accurate discriminator. This takes a long time, and will have to be updated whenever the physical variables of the experimental apparatus change.

    \item The primary intention of many dark matter experiments, which is to reduce the number of background events to the lowest level possible, means that there will be a very small number detected. This places a significant constraint on the amount of data that is available to optimize such a discriminator.

@@

The architecture described may have wider applications to several similar cases, such as those that require a discriminator which is difficult to construct using conventional techniques.

@@

The PICO-60 bubble chamber experiment, created for the detection of weakly interacting massive particles (WIMPs) \cite{pico}, was completed in 2017. It provides an excellent basis on which to develop and test the efficacy of such techniques as a potential tool for event discrimination, relative to the conventional techniques used during initial analysis of the experiment.

WIMP candidates in the cross-section and mass ranges to which the PICO-60 detector is sensitive are predicted to produce nuclear recoils with the same properties as those induced by neutrons. The key difference is that neutrons frequently (but not always) scatter several times and produce multiple bubbles, where the extremely small predicted cross-sections of WIMP candidates mean that they should almost invariably create just one bubble. This means single-bubble neutron events can be used to optimize a discriminator to detect WIMP events.

@@

The Acoustic Parameter method (abbreviated AP) is the technique that was used for event discrimination in the original PICO-60 analysis. A function was defined that discriminates between alpha particles and nuclear recoils based on audio data. It was derived based on a physical model of the bubble chamber, and was tuned using neutron calibration sources to produce events in the PICO-60 apparatus.

Before the Acoustic Parameter can be calculated, the audio data must first be converted into the frequency domain (specifically, with the banded Fourier transform $\beta_{8}$). It must also be preprocessed with the position correction function $PosCor(\beta_{8}, \chi)$, which adjusts the overall volume of an audio recording according to its position in the vessel. This is done because the acoustic characteristics differ significantly depending on the position of an event in the vessel.

@@

The lowest-level data derived from the piezos is the raw waveform $\omega$. This consists of a series of samples collected every $2.5 \times 10^{-6}$ seconds. They are each represented as a 16-bit integer. Only the section of the audio between sample 90,000 (inclusive) and sample 190,000 (exclusive) was used during most experiments, because there is only background noise prior to this window, and a clipped signal produced by hydraulics repressurizing the vessel after. (These sections contain no information and can be undesirably fit on by neural networks.)

@@

The raw waveform $\omega$ was converted into the frequency domain by means of a one-dimensional Discrete Fourier Transform (DFT) for real input. Since DFTs produce sequences of complex numbers, the magnitude of each element was computed. The direct output from such a DFT is the full-resolution Fourier transform $\beta _{50,001}$, which consists of a sequence of numbers half the length of the raw waveform $\omega$. (It is half the length because the output of a DFT of real inputs is Hermitian, meaning there is no new information contained in the second half of the output.)

Beyond this, the banded Fourier transform $\beta_{8}$ (which is the input to Acoustic Parameter and the original neural analysis) was computed by integrating the resonant energy over all frequencies within each of a set of bands. This can be thought of as a method of signal downscaling, compressing the information into a smaller number of data points.

This process was generalized to several other banding resolutions. Higher-resolution counterparts of $\beta_{8}$ included $\beta_{20}$ and $\beta_{40}$.

@@

For each event that is captured, the four cameras within the PICO-60 apparatus each capture a sequence of 71 images before and after formation of a bubble is detected using the cameras and an entropy-based trigger. These raw images contain a large amount of extraneous information; they encompass the entire vessel. To reduce the input information, the image window sequence $\iota$ includes 50\texttimes50 cropped windows around the position of the bubble. The 71 frames, many of which contain either no bubble or a bubble in later stages of formation, are reduced to 10 immediately around the formation of the bubble. Five frames from before the recording trigger are included in $\iota$, because the bubble does not cause a trigger until it is already of a significant size.

@@

\begin{itemize}
    \item The run was not collected during engineering or testing
    \item Recording was triggered by the camera
    \item Acoustic Parameter is not erroneously large and negative ($log_{10}(AP)>-100$)
    \item Recorded more than 25 seconds after reaching target pressure
    \item The bubble position $\chi$ was successfully calculated ($[\chi_{X}, \chi_{Y}, \chi_{Z}]\neq[-100, -100, -100]$)
\end{itemize}

@@

\begin{itemize}
    \item Either 0 or 1 bubbles are detected based on images from the camera
    \item The number of bubbles approximated using the pressure transducer is close to 1
\end{itemize}

@@

\begin{itemize}
    \item The fiducial cut $FidWallCut(D)$ defines a spatial area along the walls of the vessel within which no events are accepted. It determines whether events fall within this area based on the visually calculated position $\chi$.
    \item The pressure cut $PresWallCut(D)$ restricts the pressure detected by the pressure transducer, without any position corrections, to be within a range of 0.3 of 1
    \item The acoustic cut $AcWallCut(D)$ is defined using the banded Fourier transform $\beta_{8}$, and takes advantage of differences in the frequency distribution (specifically the first and second frequency bands of the first and third piezos) of wall events and non-wall events.
\end{itemize}

@@

\begin{itemize}
    \item Supervised learning, in which a system is trained on a set of fully-labeled data to classify unseen examples according to the patterns it observes in the training set, and
    \item Unsupervised learning, in which a system finds patterns or clusters in a set of unlabeled data. This can find order in almost any training set, but it is unpredictable and may not find the particular patterns desired.
\end{itemize}

A significant challenge in this application is that neither supervised nor unsupervised learning is ideal. The calibration sets available for training are not pure, so supervised learning is likely to overfit on biases and produce undesirable results. Conversely, unsupervised learning may be able to find clusters in the data, but it is impossible to guarantee that it will distinguish between nuclear recoils and alpha particles as opposed to some other binary separation.

@@

Each of the learning algorithms used in this study applies a neural network. For each of the general configurations (multi-layer perceptron, one-dimensional convolutional neural network, et cetera) there are many possible specific architectures with different hyperparameters, which have to be optimized to improve performance. Specific hyperparameters that were optimized include:

\begin{itemize}
    \item Number of layers of each type (dense, convolutional)
    \item Number of neurons in dense layers
    \item Number of filters in convolutional layers (depth of output tensor)
    \item Kernel size in convolutional layers (spatial area that a single filter covers)
    \item Stride in convolutional layers (spacing between kernel positions during convolution)
    \item Dropout regularization parameter (proportion of neurons to randomly remove for any given training example)
    \item L2 regularization $\lambda$ (multiplier for squared weights before adding to loss function)
\end{itemize}

@@

For some experimental runs, $WallCut(D)$ was not applied. This was done for 2 reasons:

@@

All supervised learning configurations were trained and evaluated based on their ability to determine the origin of events: whether they are from calibration runs (predominantly neutrons) or background runs (predominantly alpha particles). This metric was used for training and testing instead of Acoustic Parameter for two reasons:

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{waveform_hist}
    \caption{\label{waveform_hist} Prediction distribution of the best $DeepConvWithPos(\omega, \chi)$ discriminator without $WallCut(D)$. (Validation Event Count is the number of events in the validation set that fall within a certain network prediction band.)}
\end{figure}

@@

\begin{center}
    \captionof{table}{$DeepConvWithPos(\omega, \chi)$ with $WallCut(D)$.}
    \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        L2 $\lambda$ & Dropout & Filters & Kernel Size & \# Layers Multiplier & Max Accuracy & Class-Wise Std Dev \\
        \hline
        0.003 & 0 & 24 & 3 & 3 & 95\% & 0.44 \\
        \hline
        0.003 & 0 & 48 & 5 & 3 & 96\% & 0.41 \\
        \hline
        0.003 & 0.5 & 24 & 5 & 3 & 93\% & 0.50 \\
        \hline
        0.001 & 0 & 48 & 5 & 3 & 95\% & 0.48 \\
        \hline
        0.001 & 0.25 & 48 & 3 & 6 & 93\% & 0.62 \\
        \hline
        0.0003 & 0.5 & 24 & 5 & 6 & 95\% & 0.49 \\
        \hline
    \end{tabular}

    \captionof{table}{$DeepConvWithPos(\omega, \chi)$ without $WallCut(D)$.}
    \begin{tabular}{|l|l|l|l|l|l|l|}
        \hline
        L2 $\lambda$ & Dropout & Filters & Kernel Size & \# Layers Multiplier & Max Accuracy & Class-Wise Std Dev \\
        \hline
        0.003 & 0 & 24 & 3 & 3 & 91\% & 0.61 \\
        \hline
        0.003 & 0.5 & 24 & 5 & 3 & 91\% & 0.65 \\
        \hline
        0.001 & 0.25 & 24 & 3 & 3 & 91\% & 0.66 \\
        \hline
        0.001 & 0.5 & 48 & 5 & 3 & 88\% & 0.73 \\
        \hline
        0.0003 & 0 & 48 & 5 & 6 & 78\% & 0.95 \\
        \hline
        0.0003 & 0.5 & 48 & 5 & 6 & 74\% & 0.92 \\
        \hline
    \end{tabular}
\end{center}

@@

In addition to the Fourier transform used in the original PICO-60 analysis, higher resolutions were computed by similar means. These included $\beta _{20}$ and $\beta _{40}$. Also, the full-resolution $\beta _{50,001}$ was input into a neural network directly, without any downscaling.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{banded_no_pos_input_hist}
    \caption{\label{banded_no_pos_input_hist} Prediction distribution of the best $FourierMLP(\beta_{8})$ discriminator, with $WallCut(D)$.}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{high_freq_no_wall_hist}
    \caption{\label{high_freq_no_wall_hist} Prediction distribution of the best $FourierMLPWithPos(\beta_{50,001}, \chi)$ discriminator, without $WallCut(D)$.}
\end{figure}

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Neural networks trained on Fourier transforms with $WallCut(D)$.} \label{fft_wall_cuts}
        \begin{tabular}{|l|l|l|l|l|l|}
            \hline
            Configuration & L2 $\lambda$ & Dropout & Layers & Max Accuracy & Class-Wise Std Dev \\
            \hline
            $FourierMLP(PosCor(\beta_{8}))$ & 0 & 0.5 & 2 & 95\% & 0.56 \\
            \hline
            $FourierMLP(\beta_{8})$ & 0 & 0.5 & 2 & 98\% & 0.29 \\
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.5 & 3 & 95\% & 0.44 \\
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 0 & 0.25 & 3 & 97\% & 0.43 \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0.003 & 0.25 & 3 & 93\% & 0.54 \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 94\% & 0.52 \\
            \hline
            $FourierMLPWithPos(\beta_{40}, \chi)$ & 0 & 0 & 3 & 91\% & 0.57 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.0003 & 0 & 4 & 91\% & 0.53 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.25 & 4 & 91\% & 0.56 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0.5 & 3 & 89\% & 0.64 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 4 & 89\% & 0.65 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$FourierMLPWithPos(\beta{N})$ trained without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|l|l|l|}
            \hline
            Configuration & L2 $\lambda$ & Dropout & Layers & Max Accuracy & Class-Wise Std Dev \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 0 & 0 & 3 & 92\% & 0.63 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0 & 0 & 3 & 95\% & 0.49 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.001 & 0 & 2 & 96\% & 0.47 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0 & 2 & 97\% & 0.47 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.25 & 2 & 95\% & 0.54 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 0.01 & 0.5 & 2 & 94\% & 0.53 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

It is very clear in Table \ref{fft_wall_cuts} that higher resolutions do not improve accuracy. Regularization, both dropout and L2, appears to have relatively little effect.

@@

\begin{center}
    \captionof{table}{Performance of $ImageConv(\iota)$ configurations, trained without $WallCut(D)$.}
    \begin{tabular}{|l|l|l|l|l|l|}
        \hline
        L2 $\lambda$ & Dropout & Convolutional Layers & Dense Layers & Max Accuracy & Class-Wise Std Dev \\
        \hline
        0 & 0.5 & 4 & 3 & 77\% & 1.01 \\
        \hline
        0 & 0.25 & 4 & 3 & 85\% & 0.95 \\
        \hline
        0.01 & 0.25 & 4 & 3 & 66\% & 0.97 \\
        \hline
        0.003 & 0.25 & 4 & 3 & 69\% & 0.97 \\
        \hline
        0.01 & 0.25 & 12 & 3 & 66\% & 0.98 \\
        \hline
        0.01 & 0.5 & 12 & 3 & 68\% & 0.99 \\
        \hline
    \end{tabular}
\end{center}

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Summary of supervised learning configurations, trained with $WallCut(D)$.}
        \begin{tabular}{|l|l|l|}
            \hline
            Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
            \hline
            $FourierMLP(PosCor(\beta_{8}), \chi)$ & 97\% & 0.42 \\
            \hline
            $FourierMLP(\beta_{8})$ & 98\% & 0.29 \\
            \hline
            $FourierMLPWithPos(\beta_{8}, \chi)$ & 95\% & 0.44 \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 94\% & 0.52 \\
            \hline
            $FourierMLPWithPos(\beta_{40}, \chi)$ & 91\% & 0.54 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 91\% & 0.53 \\
            \hline
            Original PICO-60 Neural Network & 94\% & 0.99 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Summary of supervised learning configurations, trained without $WallCut(D)$.}
        \begin{tabular}{|l|l|l|}
            \hline
            Configuration & Max Accuracy & Mean Class-Wise Standard Deviation \\
            \hline
            $FourierMLPWithPos(\beta_{20}, \chi)$ & 92\% & 0.63 \\
            \hline
            $FourierMLPWithPos(\beta_{50,001}, \chi)$ & 97\% & 0.47 \\
            \hline
            $DeepConv(\omega)$ & 77\% & 0.86 \\
            \hline
            $DeepConvWithPos(\omega, \chi)$ & 91\% & 0.61 \\
            \hline
            $ImageConv(\iota)$ & 85\% & 0.95 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}
